---
title: "R Notebook"
output: html_notebook
---

ACME EMPLOYEES

The database have three tables:
  *employees: this have 5 columns
    *id -> integer and PK
    *first_name -> varchar
    *last_name -> varchar 
    *email -> varchar
    *team -> id FK from teams table
  *teams: this have 3 columns 
    *id -> integer PK
    *name -> varchar
    *charge_cost -> integer
  *feed_back:this have 3 columns
    *id -> integer PK
    *id_employee -> integer FK from employees
    *message -> varchar
    *date -> date
The relation ship between tables are

employees Many<---->One teams
employee One<---->Many feedbacks

```{r}
#libraries that I will use
library(keyring)
library(RPostgreSQL)
```
```{r}
#Making my connection with keychain 
keyring_unlock(keyring = "local")
username <- key_get(service = "postgresql_username", keyring = "local")
password <- key_get(service = "postgresql_password", keyring = "local")
keyring_lock(keyring = "local")
```
```{r}
#coneccting with my da
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 1), user = username, password = password, dbname='acme_employees', host='localhost')
```
Data Frame of employees 200 rows 5 columns
```{r}
employees_acme <- data.frame(
                  dbGetQuery(conn = my_db_connection,
                             statement = 
                               "SELECT *
                                FROM employees;")
)
```
All employees with full name
```{r}
dbGetQuery(conn = my_db_connection, 
           statement = 
             "SELECT id, concat(first_name, ' ' ,last_name) as full_name, email, team_id
              FROM employees;")
```
All employees with the name of the team that they work
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             'SELECT employees.id, employees.first_name, employees.last_name, employees.email, 
              teams.name AS team_name
              FROM employees
              LEFT JOIN teams
              ON employees.team_id = teams.id;')
```
All the employees per team with desc order and team even teams without employees
```{r}
dbGetQuery(conn = my_db_connection, 
           statement = 
             "SELECT teams.name AS team_name, count(employees.id)AS num_employees
              FROM employees
              RIGHT JOIN teams
              ON employees.team_id = teams.id
              GROUP BY teams.id
              ORDER BY num_employees DESC NULLS LAST;")
```
Employees without email or not valid email
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT count(id) as employees_without_email_or_valid_email
              FROM employees
              WHERE email NOT LIKE '%@%' OR email IS NULL;")
```
Employees with the last feedback
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT employee_id, concat(employees.first_name, ' ', employees.last_name) AS   
              full_name, feedbacks.date AS feed_back_date, feedbacks.message AS feed_back_message
              FROM employees
              INNER JOIN feedbacks
              ON employees.id = feedbacks.employee_id
              ORDER BY feedbacks.date DESC
              LIMIT 1;")
```
Employees with only initial letter as fist_name
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT teams.name AS team_name, count(employees.id) 
              AS employees_with_only_initial_letter_first_name
              FROM employees
              INNER JOIN teams
              ON employees.team_id = teams.id
              WHERE employees.first_name LIKE '_'
              GROUP BY teams.id
              ORDER BY count(employees.id) DESC
              LIMIT 1;")
```
Sentimental analyst
```{r}
data_feedback <- data.frame(dbGetQuery(conn = my_db_connection,
                statement = 
                "SELECT employees.id, 
                concat(employees.first_name, ' ', employees.last_name) AS full_name_employee, 
                feedbacks.message, feedbacks.date AS feedback_date
                FROM employees
                INNER JOIN feedbacks
                ON employees.id = feedbacks.employee_id;"))
```
take out the puntuation adn convert to low case
```{r}
message <- gsub("[[:punct:]]", " ", data_feedback$message)
message_lower <- tolower(message)
message_lower
```
create positive and negative vector
```{r}
positive_words <- c("great", "good", "happy", "content", "fulfilled", "fulfilled", "positive", "positives", "cheerful", "nice", "ambition", "ambitions", "ambitious", "friendly", "progress", "joy", "fast", "achieve", "achieving", "achievements", "best", "better",  "unlimited", "pros", "competitive", "opportunity", "advancement", "friendly", "smart", "interesting", "challenging", "grow", "caring", "balance", "helpful")

negative_words <- c("worse", "worsening", "worst", "slow", "sluggish", "impatient", "unfulfilled", "unfulfilling", "negative", "bad", "limited", "limit", "limitations", "cons", "frustrated", "frustrating", "frustration", "dull", "boring", "politics", "political", "ignore", "ignored", "ignoring", "sad", "depressed", "depressing", "nasty", "stress", "stresses", "stressed", "horrid", "horrible", "terrible", "deadline", "deadlines", "uncaring", "remote")
```

```{r}
#x vector to try, x_evaluation vector with the parameters, i indicate if it is postive of negative
puntuation <- function(x_vector, x_evaluation, i){
  x_vector_return <-0
  for(j in 1:length(x_vector)){
    x_vector_return[j] <- 0
    for(h in 1:length(x_evaluation)){
      x_vector_return[j] <- stringr::str_count(x_vector[j], x_evaluation[h]) + x_vector_return[j]
    }
  }
  return(x_vector_return * i)
}
puntuation_positive <- puntuation(message_lower, positive_words, 1)
puntuation_positive
puntuation_negative <- puntuation(message_lower, negative_words, -1)
puntuation_negative 
total_puntuation <- puntuation_positive + puntuation_negative
total_puntuation
```

```{r}
data_feedback <- cbind(data_feedback, total_puntuation)
```
```{r}
data_feedback_team <- RPostgreSQL::dbGetQuery(conn = my_db_connection,
                        statement = 
                          "SELECT e_f.*, teams.name AS team_name
                            FROM teams
                            INNER JOIN (SELECT employees.id, employees.team_id,
                            concat(employees.first_name, ' ', employees.last_name) AS   
                            full_name_employee, 
                            feedbacks.message, feedbacks.date AS feedback_date
                            FROM employees
                            INNER JOIN feedbacks
                            ON employees.id = feedbacks.employee_id) AS e_f
                            ON teams.id = e_f.team_id;")
data_feedback_team <- cbind(data_feedback_team, total_puntuation)
```
```{r}
data_feedback_team[order(-data_feedback_team$total_puntuation),]
for(i in 1:length(data_feedback_team$total_puntuation)){
  if(data_feedback_team$total_puntuation[i] == max(data_feedback_team$total_puntuation)){
  print(data_feedback_team[i, ])
  }
}
for(i in 1:length(data_feedback_team$total_puntuation)){
  if(data_feedback_team$total_puntuation[i] == min(data_feedback_team$total_puntuation)){
  print(data_feedback_team[i, ])
  }
}
```





```{r}
#disconect
dbDisconnect(my_db_connection)
```

