---
title: "Homework Week 5 Day 2"
author: "Sandra Tobon"
date: "07/04/2020"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: styles.css
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(tidyverse)
library(CodeClanData)
library(lubridate)
```
<center>
# Homework ggplot2 Advance   
</center>

## MVP  

  1. Revenue across the two years in the dataset  
  
```{r}
col_scheme <- c("#E89FE9", "#50434F", "#B6A7B5", "#F9A472", "#BD7040")

ggplot(qb_revenue_breakdown) +
  aes(x = Year, y = Revenue, fill = Product) +
  geom_bar(stat = "identity", position="stack") +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£")) +
  scale_fill_manual(values = col_scheme) +
  labs(
    title = "QikBit Revenue 2018 - 2019",
    subtitle = "By Product",
    x = "Time (years)"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12, face = "italic"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 8),
    legend.title = element_text(size = 12),
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )
```
  
  2. Make a line chart showing monthly sales of the “flagship product” - the KwikBit Unit1 - over the last year  
  
```{r}

qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  mutate(Cashflow = recode(Cashflow, "Kwikbit Unit 1 Sales" = "Kwikbit Unit 1")) %>%
  ggplot() +
  aes(x = Date, y = Amount, colour = Cashflow) +
  geom_line() +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£"), limits = c(0, 700)) +
  scale_color_manual(values = col_scheme) +
  labs(
    title = "KwikBit Unit1 sales (£)",
    colour = "Product",
    x = "Time (months)"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )

```
  
  3. Line chart showing monthly revenue and costs over the last year  
  
```{r}
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  mutate(Cashflow = recode(Cashflow, "Total Revenue" = "Revenue")) %>%
  ggplot() +
  aes(x = Date, y = Amount, colour = Cashflow) +
  geom_line() +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£"),
                     limits = c(0, 3000)) +
  scale_color_manual(values = col_scheme[4:5]) +
  labs(
    title = "QikBit Revenue and Costs",
    x = "Time (months)",
    colour = ""
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12, face = "italic"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 8),
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )

```

  4. Show annual sales of personal fitness trackers over the last 5 years broken down by company as a ribbon plot.  
  
```{r}
qb_competitors %>%
ggplot() +
  aes(x = Year, y = Revenue, fill = Company) +
  geom_area() +
  scale_fill_manual(values = col_scheme[2:5]) +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£")) +
  labs(
    title = "Fitness tracker sales",
    subtitle = "By competitor, between 2015 and 2019",
    x = "Time (years)\n",
    y = "Revenue \n",
    fill = ""
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12, face = "italic"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 8), 
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )
```

  5. The sales from the 5 competitors as a line graph. Include an extra layer that shows the data points used to make the lines.

```{r}
qb_competitors %>%
  ggplot() +
  aes(x = Year, y = Revenue, color = Company) +
  geom_line() +
  geom_point() +
  scale_color_manual(values = col_scheme[2:5]) +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£")) +
  labs(
    title = "Fitness tracker sales",
    subtitle = "By competitor, between 2015 and 2019",
    x = "Time (years)\n",
    y = "Revenue \n",
    color = ""
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12, face = "italic"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 8), 
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )
```

  6. Number of steps that their device counts vs. their competitors.  
  
```{r}
qb_device_data %>%
  mutate(hours = hours + (mins/60)) %>%
  ggplot() +
  aes(x = hours, y = counts, color = id) +
  geom_line() +
  facet_grid(device~id) +
  scale_color_manual(values = col_scheme) +
  labs(
    title = "Accuracy of stepcount devices",
    subtitle = "Comparison of four different devices across five people",
    x = "Time (hours)\n",
    y = "Number of steps \n",
    colour = ""
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12, face = "italic"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 8), 
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )
```
  
## Extensions  
```{r}
qb_monthly_sales %>%
  filter(Cashflow == "Kwikbit Unit 1 Sales") %>%
  mutate(Cashflow = recode(Cashflow, "Kwikbit Unit 1 Sales" = "Kwikbit Unit 1")) %>%
  ggplot() +
  aes(x = Date, y = Amount, fill = Cashflow) +
  geom_histogram( stat = "identity") +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£"), limits = c(0, 700)) +
  scale_fill_manual(values = col_scheme) +
  labs(
    title = "KwikBit Unit1 sales (£)",
    fill = "Product",
    x = "Time (months)"
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.text = element_text(size = 8),
    axis.title = element_text(size = 12),
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )
```


```{r}
qb_monthly_sales %>%
  filter(Cashflow != "Kwikbit Unit 1 Sales") %>%
  mutate(Cashflow = recode(Cashflow, "Total Revenue" = "Revenue")) %>%
  ggplot() +
  aes(x = Date, y = Amount, fill = Cashflow) +
  geom_histogram(stat = "identity", position = "stack") +
  scale_y_continuous(labels = scales::dollar_format(prefix = "£")) +
  scale_fill_manual(values = col_scheme[4:5]) +
  labs(
    title = "QikBit Revenue and Costs",
    x = "Time (months)",
    fill = ""
  ) +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12, face = "italic"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 8),
    legend.title  = element_text(size = 12), 
    legend.text = element_text(size = 12), 
    panel.grid = element_line(colour = "lightgrey")
  )
```

