---
title: "R Notebook"
output: html_notebook
---
```{r}
keyring_unlock(keyring = "local")
```
Create a connection
```{r}
username <- key_get(service = "postgresql_username", keyring = "local")
password <- key_get(service = "postgresql_password", keyring = "local")
keyring_lock(keyring = "local")
```

```{r}
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = username, password = password, dbname='wrestling', host='localhost')
```
```{r}
dbListFields(conn = my_db_connection, name = "wrestlers")
```
id is a unique number,
born is a varchar
name is a varchar
gender is a varchar (only 2 values)
win_percent is a real
total_matches is a int
```{r}
dbGetQuery(conn = my_db_connection,
           statement = "SELECT * 
           FROM wrestlers")
```
disconnect
```{r}
dbDisconnect(my_db_connection)
```
REMOTE CONECTION
```{r}
keyring_unlock(keyring = "remote")
```

```{r}
username <- key_get(service = "omni_postgresql_username", keyring = "remote")
password <- key_get(service = "omni_postgresql_password", keyring = "remote")
keyring_lock(keyring = "remote")
```
```{r}
my_db_connection <- dbConnect(drv = PostgreSQL(max.con = 2), user = username, password = password, dbname='mvhbdgdk', host='34.245.37.126')
```
```{r}
dbListTables(conn = my_db_connection)
```
QUERY
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT *
              FROM wrestlers")
```
EXTENSION
```{r}
dbListFields(conn = my_db_connection, name = 'wrestlers')
```

ALL THE wrestlers FROM UK
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT *
              FROM wrestlers
              WHERE born = 'United Kingdom'")
```

Names of all Japanese wrestlers who have appeared in 40 or more matches.
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT name
              FROM wrestlers
              WHERE born = 'Japan' AND total_matches >= 40")
```
Find the wrestlers who have won between 50% and 60% of their matches.
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT *
              FROM wrestlers
              WHERE win_percent BETWEEN 50 AND 60
              ORDER BY win_percent ASC")
```

Find all the wrestlers with names beginning with ‘X’.
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT *
              FROM wrestlers
              WHERE name LIKE 'X%'")
```
Find all the wrestlers who were born in countries beginning with the letter ‘I’. Try this using IN (there are 9 countries) and using a wildcard comparison.
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT * 
              FROM wrestlers 
              WHERE born IN (SELECT born
              FROM wrestlers
              WHERE born LIKE 'I%'
              GROUP BY born)")
```
Find all the wrestlers who were not born in countries beginning with the letter ‘I’
```{r}
dbGetQuery(conn = my_db_connection,
           statement = 
             "SELECT * 
              FROM wrestlers 
              WHERE born NOT IN (SELECT born
              FROM wrestlers
              WHERE born LIKE 'I%'
              GROUP BY born)")
```

