---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(leaps)
library(GGally)
library(modelr)
library(rpart)
library(rpart.plot)
library(yardstick)
```

```{r}
avocado <- clean_names(read_csv(here("data/avocado.csv")))
```
```{r}
avocado <- avocado %>%
  mutate(region = case_when(
    region %in% c("California", "LasVegas", "LosAngeles", "Portland", "Sacramento", "SanDiego", "SanFrancisco", "Seattle", "Spokane", "West") ~ "FarWest",
    region %in% c("Chicago", "CincinnatiDayton", "Columbus", "Detroit", "GrandRapids", "GreatLakes", "Indianapolis") ~ "GreatLakes",
    region %in% c("Albany", "BaltimoreWashington", "BuffaloRochester", "HarrisburgScranton", "NewYork", "Northeast", "Philadelphia", "Pittsburgh", "Syracuse") ~ "Mideast",
    region %in% c("Boston", "HartfordSpringfield", "NorthernNewEngland") ~ "NewEngland",
    region %in% c("Plains", "StLouis") ~ "Plains",
    region %in% c("Boise", "Denver") ~ "Rocky Mountain",
    region %in% c("Atlanta", "Charlotte", "Jacksonville", "Louisville", "MiamiFtLauderdale", "Midsouth", "Nashville", "NewOrleansMobile", "Orlando", "RaleighGreensboro", "RichmondNorfolk", "Roanoke", "SouthCarolina", "Southeast", "Tampa") ~ "Southeast",
    region %in% c("DallasFtWorth", "Houston", "PhoenixTucson", "SouthCentral", "WestTexNewMexico") ~ "Southwest",
    TRUE ~ region
  ))

avocado <- avocado %>%
    mutate_at("year", as.factor) %>%
    mutate(month = month(date)) %>%
    mutate(season = case_when(month >= 3 & month < 6 ~ "Spring",
                              month >= 6 & month < 9 ~ "Summer",
                              month >= 9 & month < 12 ~ "Fall",
                              TRUE ~ "Winter"
                              )) %>%
    select(- c(month, date, x1))
```

```{r}
avocado <- avocado %>%
  mutate(organic = as.factor(ifelse(type == "organic", "Yes", "No"))) %>%
  mutate_if(is.character, as.factor) %>%
  select(-type)
dim(avocado)
```
We have quite a lot data so we can have a test set of 20% of the data
```{r}
avocado %>%
  select(region, season, organic, year) %>%
  ggpairs()
```
Region is the only varaible that look correlated with organic year somehow could be correlated but only because we don't have a lot information about 2018.
```{r}
avocado %>%
  select(-c(region, season, year)) %>%
  ggpairs()
```
Average price in the one that look more correlated
```{r}

n_data <- nrow(avocado)

text_index <- sample(1:n_data, size = n_data * 0.2)

avocado_train <- slice(avocado, -text_index)

avocado_test <- slice(avocado, text_index)
```

```{r}
avocado_test %>%
  tabyl(organic)
avocado_train %>%
  tabyl(organic)
```

```{r}
organic_fit <- rpart(organic ~ ., 
                     data = avocado_train,
                     method = "class")

rpart.plot(organic_fit, yesno = 2)
```
if Total volume >= 69000, if the avocado x477 >=13 (volume) and the average price < 1.5 the probability of no organic is 0.03
if Total volume >= 69000, if the avocado x477 >=13 (volume) and the average price >= 1.5 and the large bag >= 0.56 the probability of no organic is 0.07
if Total volume >= 69000, if the avocado x477 >=13 (volume) and the average price >= 1.5 and the large bag < 0.56 the probability of organic is 0.64
if Total volume >= 69000, if the avocado x477 < 13 (volume) the probability of organic is 0.93
if Total volume < 69000 the probability of organic is 0.97
```{r}
summary(organic_fit)
```

```{r}
organic_predic <- avocado_test %>%
  add_predictions(organic_fit, type = "class")
```

```{r}
organic_predic %>%
  select(organic, pred)
```

```{r}
organic_predic %>%
  conf_mat(truth = organic,
           estimate = pred)
```

```{r}
organic_predic %>%
  accuracy(truth = organic,
           estimate = pred)
```

The accuracy is 0.95 it doesn't look too bad and also the the false negative a positive aren't too much.
total_volume    total_bags         x4225    small_bags         x4770         x4046 average_price 
           19            17            16            16            16            14             1 
 x_large_bags 
```{r}
organic_fit_1 <- rpart(organic ~ total_volume + total_bags + x4225 + x4770 + x4046 + average_price, 
                     data = avocado_train,
                     method = "class")

rpart.plot(organic_fit_1, yesno = 2)
```
 
```{r}
organic_predic_1<- avocado_test %>%
  add_predictions(organic_fit_1, type = "class")

```
 
```{r}
organic_predic_1 %>%
  conf_mat(truth = organic,
           estimate = pred)
```
```{r}
organic_predic_1 %>%
  accuracy(truth = organic,
           estimate = pred)

```
 This one is with less predictors (those that have more importance in the first model), probably this will prevent the overffitng and continue to have quite a good fit
 