---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(here)
library(factoextra)
library(broom)
```


```{r}
computer <- read_csv(here("data/computers.csv"))

computer <- computer %>%
  unite(price, c(price, X1), sep = ":") 
```

```{r}
computer_scale <- computer %>%
  select(hd, ram, price) %>%
  mutate_if(is.numeric, scale) %>%
  column_to_rownames("price")

computer_scale %>%
  ggplot(aes(x = hd, y = ram)) +
  geom_point() 
```
Some points are very concentrate special in the ram lower to 0, so probably it will work but some cluster we will have more points that others

```{r}
fviz_nbclust(computer_scale, kmeans, method = "wss", nstart = 25)
```
With Elbow method K means of 3 or 4 look acceptable
```{r}
fviz_nbclust(computer_scale, kmeans, method = "silhouette", nstart = 25)
```
 Silhouette coefficient proupose k means of 10
```{r}
fviz_nbclust(computer_scale, kmeans, method = "gap_stat", nstart = 25, k.max = 12)
```
We will choose 7 it is in the middle and look also good in the Silhouette method 

```{r}
cluster_computer <- kmeans(computer_scale, centers = 7, nstart = 25)
cluster_computer
```
```{r}
tidy(cluster_computer,
     col.names = colnames(computer_scale))
```

```{r}
glance(cluster_computer)
```

```{r}
augment(cluster_computer, computer_scale)
```
```{r}
max_k <- 10

k_clusters <- tibble(k = 1:max_k) %>%
  mutate(
    kclust = map(k, ~ kmeans(computer_scale, .x, nstart = 25)), 
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, computer)
  )

k_clusters
```

```{r}
clusterings <- k_clusters %>%
  unnest(glanced)

clusterings
```
```{r}
clusterings %>% 
  unnest(cols = c(augmented)) %>%
  filter(k <= 10) %>%
 ggplot(aes(x = hd, y = ram)) +
  geom_point(aes(color = .cluster)) + 
  facet_wrap(~ k)
```

With 7 the clusters look ok with 10 we have clusters with only 2 points, with 2 the partition doesn't look to logical special for the point that have a ram of 15. 