---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(here)
library(janitor)
library(lubridate)
library(leaps)
```


```{r}
avocado_data <- read_csv(here("data/avocado.csv"))
avocado_data <- clean_names(avocado_data)
```
I will include the regions but I will group by them by the economic division region in USA
```{r}
avocado_data <- avocado_data %>%
  mutate(region = case_when(
    region %in% c("California", "LasVegas", "LosAngeles", "Portland", "Sacramento", "SanDiego", "SanFrancisco", "Seattle", "Spokane", "West") ~ "FarWest",
    region %in% c("Chicago", "CincinnatiDayton", "Columbus", "Detroit", "GrandRapids", "GreatLakes", "Indianapolis") ~ "GreatLakes",
    region %in% c("Albany", "BaltimoreWashington", "BuffaloRochester", "HarrisburgScranton", "NewYork", "Northeast", "Philadelphia", "Pittsburgh", "Syracuse") ~ "Mideast",
    region %in% c("Boston", "HartfordSpringfield", "NorthernNewEngland") ~ "NewEngland",
    region %in% c("Plains", "StLouis") ~ "Plains",
    region %in% c("Boise", "Denver") ~ "Rocky Mountain",
    region %in% c("Atlanta", "Charlotte", "Jacksonville", "Louisville", "MiamiFtLauderdale", "Midsouth", "Nashville", "NewOrleansMobile", "Orlando", "RaleighGreensboro", "RichmondNorfolk", "Roanoke", "SouthCarolina", "Southeast", "Tampa") ~ "Southeast",
    region %in% c("DallasFtWorth", "Houston", "PhoenixTucson", "SouthCentral", "WestTexNewMexico") ~ "Southwest",
    TRUE ~ region
  ))
```

```{r}
avocado_data %>%
  group_by(date) %>%
  summarise(a_p = mean(average_price)) %>%
  ggplot(aes(x = date, y = a_p)) +
  geom_line()
```

The average price has a seasonal component so we shouldn't exclude the date at least that we transform the date in a categorical variable that give us the season. We will keep the year as categorical data because the average price has increased with the time in each season.

```{r}
avocado_data <- avocado_data %>%
    mutate_at("year", as.factor) %>%
    mutate(month = month(date)) %>%
    mutate(season = case_when(month >= 3 & month < 6 ~ "Spring",
                              month >= 6 & month < 9 ~ "Summer",
                              month >= 9 & month < 12 ~ "Fall",
                              TRUE ~ "Winter"
                              )) %>%
    select(- c(month, date, x1))
```
The total bags is a derivate variable from small_bags, large_bags, x_large_bags and even when alias doesn't give me any correlation.
```{r}
alias(average_price ~., data = avocado_data)

avocado_data <- avocado_data %>%
  select(- total_bags)
```
Now I believe that my data is in a good shape, so I will try to see wath happen with leap 
```{r}
regsubsets_avocado <- regsubsets(average_price ~., data = avocado_data, 
                                 nvmax = 13, method = "forward")
```

```{r}
sum_regsubsets_forward<- summary(regsubsets_avocado)
plot(regsubsets_avocado, scale = "adjr2")
```

