---
title: "R Notebook"
output: html_notebook
---

```{r}
library(rpart)
library(rpart.plot)
library(tidyverse)
library(here)
library(GGally)
library(modelr)
library(janitor)
library(yardstick)
```


```{r}
titanic_set <- read_csv(here("data/titanic_decision_tree_data.csv"))
head(titanic_set)
summary(titanic_set)
```

We have 418 NA in survived and 263 in age also 1 in fare
```{r}
titanic_set <- titanic_set %>%
  drop_na(survived)
```
```{r}
titanic_set <- titanic_set %>%
  mutate_at("sex", as.factor) %>%
  mutate(survived = factor(survived, levels = c(0, 1), labels = c("No", "Yes")),
         age_status = as.factor(ifelse(age >= 16, "adult", "child")),
         pclass = factor(pclass, levels = c(1, 2, 3),
                        labels = c("Upper Class","Middle Class", "Lower Class")),
         embarked = factor(embarked, levels = c("S", "C", "Q"), 
                           labels = c("Cherbourg", "Queenstown", "Southampton")))

titanic_set <- titanic_set %>%
  select(-c(X1, passenger_id, name, age, ticket, fare, cabin)) %>%
  drop_na()
```

```{r}
  ggpairs(titanic_set)
```
Probably survived is related with age status, because more adults died in proportion with the childs, for sure sex is high correlated and also pclass look a litle related. Let's see what happen

```{r}
dim(titanic_set)
```
We have 712 rows, I will only use the 10 % of my data for testing.
```{r}
n_data <- nrow(titanic_set)

text_index <- sample(1:n_data, size = n_data * 0.1)

titanic_test <- slice(titanic_set, text_index)

titanic_train <- slice(titanic_set, - text_index)
```

```{r}
titanic_test %>%
  tabyl(survived)
```
```{r}
titanic_train %>%
  tabyl(survived)
```
This division look very good so we go with them
```{r}
titanic_fit <- rpart(survived ~.,
                     data = titanic_train,
                     method = "class")
rpart.plot(titanic_fit, yesno = 2)

summary(titanic_fit)
```
The sex, class are the more important follow by age and embarked and in the botom number or siblings aboard.
This Say probability or survived = no 0.4, if he is male and if he is in middle or lower class and he is an adult his probability of died is 11%
if he is male and if he is in middle or lower class and he is a child and he has 3 or more siblings aboard the Titanic his probability of died is 7% 
if he is male and if he is in middle or lower class and he is a child and he doesn't has 3 or more siblings aboard the Titanic his probability of survived is 89% 
if he is male and if he isn't middle or lower class his probability of died is 42%
if she is a woman ans she is lower class and she embarked in Cherbourg or Southampton her probability of died is 39%
if she is a woman ans she is lower class and she doesn't embark in Cherbourg or Southampton her probability of survived is 73%
if she is a woman ans she isn't lower class her probability of survived is 96%
```{r}
titanic_predic <- titanic_test %>%
  add_predictions(titanic_fit, type = "class")

titanic_predic %>%
  select(survived, pred)

titanic_predic %>%
  conf_mat(truth = survived,
           estimate = pred)

titanic_predic %>%
  accuracy(truth = survived,
           estimate = pred)
```
True positive 21 (no survived)
True negative 37 (yes survived)
False positive 4 (no survived) 
False negative 9 (yes survived)

81.69% accuracy
```{r}
titanic_fit_1 <- rpart(survived ~.,
                     data = titanic_train,
                     method = "class", control=rpart.control(minsplit = 40))
#30 observation before split and decrease in the overall factor at least by 0.001
rpart.plot(titanic_fit_1, yesno = 2)

summary(titanic_fit_1)
 
```

```{r}
titanic_predic_1 <- titanic_test %>%
  add_predictions(titanic_fit_1, type = "class")

titanic_predic_1 %>%
  select(survived, pred)

titanic_predic_1 %>%
  conf_mat(truth = survived,
           estimate = pred)

titanic_predic_1 %>%
  accuracy(truth = survived,
           estimate = pred)
```

With 40 split the accuracy is a little lower but the prevention of overfitting is more and the priciples factors are sex, clas and embarked. 