---
title: "R Notebook"
output: html_notebook
---

# Homewprk Data and Times 

```{r}
library(lubridate)
library(tidyverse)
library(nycflights13)
```

```{r}
date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")
```

1. Extract the different components (year, month, mday, yday, wday) from the variable date1. Add the labels to the month and do not abbreviate the month labels. 
```{r}
date1 %>%
  year()

date1 %>%
  month(label = TRUE, abbr = FALSE)

date1 %>%
  mday()

date1 %>%
  yday()

date1 %>%
  wday()
```

2. Add 14 days to your date1 variable and store it in a variable called next_fortnight. Take away 10 years from your date2 variable, and store it in previous_decade. 
```{r}
next_fortnight <- date1 + weeks(2)  

previous_decade <- date2 - dyears(10)
```

3. Create a variable called this_year which contains today’s date. Then create an interval object which uses this_year and the previous_decade variable you made above. Store it in interval_years. 
```{r}
this_year <- today()

interval_years <- interval(this_year, previous_decade)
```
4. Change the time zone of both your date variables to “America/New_York”, and call them nyc_date1 and nyc_date2. 

```{r}
nyc_date1 <- with_tz(date1,  tzone = "America/New_York" )
  
nyc_date2 <- with_tz(date2,  tzone = "America/New_York" )
```

5. Use the flights data from the nycflights13 dataset. Make a date-time column called departure_date from the year, month, day, hour, and minute variables in the flights tibble. 

```{r}
flights %>%
  mutate(departure_date = make_datetime(year, month, day, hour, minute))
```

