---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
library(here)
```

Load
```{r}
ames <- read_csv("data/ames.csv")

ames <- clean_names(ames)
```

Plot
 The sale_price follow the normal distribution but with skewed to the right, this is possible to see also in the poxplot where we can see a lot positive outliers. 
```{r}
ames %>%
  ggplot(aes(x = sale_price)) +
  geom_histogram(aes(y =..density..), col = "white") +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = mean(ames$sale_price), 
      sd = sd(ames$sale_price)
    ),
    col = "red"
  )
```

```{r}
ames %>%
  ggplot(aes(y = sale_price)) +
  geom_boxplot()
```

Parameters sales_prices
```{r}
sales_price_stat <- ames %>%
  summarise(
    mean = mean(sale_price),
    sd = sd(sale_price)
  )
sales_price_stat
```

```{r}
results <- tibble ()

for(i in 1:1000) {
  rep_sample <- ames %>%
    rep_sample_n(size = 100, reps = 1) %>%
    ungroup() %>%
    select(sale_price)
  
  bootstrap_rep_sample <- rep_sample %>%
    specify(response = sale_price) %>%
    generate(reps = 10000, type = "bootstrap") %>%
    calculate(stat = "mean")
  
  bootstrap_ci <- bootstrap_rep_sample %>%
    get_ci(level = 0.95, type = "percentile")
  
  bootstrap_stat <- c(
    sample = i,
    lower = bootstrap_ci[1],
    uppe = bootstrap_ci[2]
  )

  
  results <- bind_rows(results, bootstrap_stat)
}
```
```{r}

results <- rename(results, "lower" = `lower.2.5%`,
                  "upper" = `uppe.97.5%`)

results <- results %>%
  mutate(popn_param_in_ci = ifelse(lower < sales_price_stat$mean &
                                     upper > sales_price_stat$mean, TRUE, FALSE))

```
My proportion is .7% lower that 95%
```{r}
results %>%
  summarise(prop_sample = mean(popn_param_in_ci) * 100)
```

Would you know ahead of time whether the CI for mean(sale_price) from your particular sample contains the correct population parameter or not?, Not because they are ramdon samples so it isn't posible that it will always contain the correct population parameter. 